---
title: "Vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
bibliography: bibliography.bib
nocite: "@*"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
knitr::opts_chunk$set(fig.width=7, fig.height=6)


```

```{r setup, include = FALSE}
library(kableExtra)
is_kumaraswamy <- function(n, a, b) {
  u <- runif(n)
  x <- (1 - (1 - u)^(1/b))^(1/a)
  return(x)
}

is_arcsine <- function(n) {
  u <- runif(n)
  x <- sin(pi * u / 2)^2
  return(x)
}


draw_histogram <- function(xs, draw_lines=TRUE, dist, a=0, b=0, 
               plot_color="skyblue", plot_border="white",
               line_color="red", line_width=2){
  #draws the histogram of values taken from the dataset
  hist(xs, prob = TRUE, col = plot_color, border = plot_border)
  #draws the pdf line of the distribution (if enabled)
  if (draw_lines) {
    y <- seq(0.001, 0.999, length.out = 1000)
    if (dist == "kumaraswamy"){
      lines(y, a*b*y^(a-1)*(1-y^a)^(b-1), col = line_color, lwd = line_width)
    } else if (dist == "arcsine"){
      lines(y, 1/(pi*sqrt(y*(1-y))), col = line_color, lwd = line_width)
    }
  }
}

kumaraswamy_moment <- function(n, a, b){
  return(b*beta(1+n/a, b))
}

draw_table <- function(xs, dist, a=0, b=0){
  if (dist == "kumaraswamy"){
    theoretical_stats <- c(kumaraswamy_moment(1, a, b), 
                           kumaraswamy_moment(2, a, b) - 
                             kumaraswamy_moment(1, a, b)^2)
  }
  else if (dist == "arcsine"){
    theoretical_stats <- c(1/2, 1/8)
  }
  dt <- data.frame(Simulated=c(mean(xs), sd(xs)^2),
                   Theoretical=theoretical_stats,
                   row.names = c("Mean", "Variance"))
  dt %>%
    kbl() %>%
    kable_material(c("striped", "hover"))
}

draw_index_scatter <- function(xs, point_color="black", point_size=0.6, alpha=0.6) {
  n <- length(xs)
  plot(1:n, xs, col = adjustcolor(point_color, alpha.f = alpha), pch = 16, 
       cex = point_size, xlab = "Index", ylab = "Simulated Value",
       main = "Index vs Value Scatterplot")
}
```

This vignette serves as a showcase of how the functions written in inverse_transformation.R can be used for simulating the Kumaraswamy distribution and arcsine distribution.

## Kumaraswamy distribution
```{r Simulating Kumaraswamy(0.7, 0.3) and drawing a histogram and a table and a scatterplot}
set.seed(1)
n <- 10000
a <- 0.7
b <- 0.3
xs <- is_kumaraswamy(n, a, b)
draw_histogram(xs, dist="kumaraswamy", a=a, b=b)

draw_index_scatter(xs)

draw_table(xs, "kumaraswamy", a, b)

draw_index_scatter(xs)
```


## Arcsine distribution
```{r Simulating arcsine distribution and drawing a histogram and a table and a scatterplot}
set.seed(1)
n <- 10000
xs <- is_arcsine(n)
draw_histogram(xs, dist="arcsine")

draw_index_scatter(xs)

draw_table(xs, "arcsine")

draw_index_scatter(xs)
```

## Regarding AI usage

ChatGPT was used in assistance for testing the functions.
Also used for general git and R commands in console and terminal.
Gemini is used to generate shiny code for app.R and server.R

## Bibliography

::: {#refs}
:::


