\documentclass{article}
% Sets the page margins to 0.75 inch as per standard requirements
\usepackage[margin=0.75in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[dvipsnames]{xcolor} % For custom colours
\usepackage{amsmath} % For math equations
\usepackage{amssymb} % For math symbols
\usepackage{natbib} % For the bibliography
\usepackage{hyperref} % For clickable links

% --- BIBLIOGRAPHY SETUP (This creates the .bib file automatically) ---
\begin{filecontents}{bibliography.bib}
@manual{RCoreTeam,
  title = {R: A Language and Environment for Statistical Computing},
  author = {{R Core Team}},
  organization = {R Foundation for Statistical Computing},
  address = {Vienna, Austria},
  year = {2024},
  url = {https://www.R-project.org/}
}

@manual{shiny,
  title = {shiny: Web Application Framework for R},
  author = {Winston Chang and others},
  year = {2024},
  note = {R package version 1.8.1},
  url = {https://CRAN.R-project.org/package=shiny}
}

@article{kumaraswamy1980,
  title = {A generalized probability density function for double-bounded random processes},
  author = {Kumaraswamy, Ponnambalam},
  journal = {Journal of Hydrology},
  volume = {46},
  number = {1-2},
  pages = {79--88},
  year = {1980},
  publisher = {Elsevier},
  doi = {10.1016/0022-1694(80)90060-5}
}

@book{voss2013intro,
  title={An introduction to statistical computing: a simulation-based approach},
  author={Voss, J.},
  year={2013},
  publisher={John Wiley \& Sons}
}

@misc{white2015template,
  title={Undergraduate project capstone proposal template},
  author={White, J.},
  year={2015},
  url={https://www.overleaf.com/latex/templates/undergraduate-project-capstone-proposal-template/rrhdkxngmwcn},
  note={Licensed under Creative Commons CC BY 4.0}
}
\end{filecontents}
% ---------------------------------------------------------------------

% Link formatting
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    citecolor=blue,
}

\begin{document}

% --- TITLE PAGE INFO ---
\begin{center}
    \LARGE{\textbf{STA380 Project Proposal}} \\
    \vspace{1em}
    \Large{Simulating Kumaraswamy and Arcsine Distributions via Inverse Transform} \\
    \vspace{1em}
    % UPDATE NAME HERE IF NEEDED
    \normalsize\textbf{Christian Jason Sumitro, Handaru Kevin Ashshidiqie, Seye, Builder} \\
    \normalsize{christian.sumitro@mail.utoronto.ca \\
    handaru.ashshidiqie@mail.utoronto.ca}\\ 
    \vspace{1em}
    \normalsize{University of Toronto, Mississauga}
\end{center}

\begin{normalsize}

\section{Project Topic}
We are proposing to create an R Shiny application that simulates the \textbf{Kumaraswamy distribution} and the \textbf{Arcsine distribution}. We will generate random variables from these distributions using the Inverse Transform Sampling method applied to the Uniform distribution.

\section{Simulation vs. Dataset}
This project will use \textbf{pure simulation}. 

We will not be using any external datasets. Instead, we will generate synthetic data in R. Specifically, we will generate $U \sim \text{Uniform}(0,1)$ and transform it using the inverse cumulative distribution functions (CDFs) derived in the details below.

\section{Project Details}
We will implement the simulation logic in R and wrap it in a Shiny interface. The goal is to verify that our simulated samples match the theoretical density curves.

\noindent \textbf{Mathematical Formulas:}
\begin{itemize}
    \item \textbf{Kumaraswamy Distribution:} Using the inverse CDF derived from:
    $$x = \left( 1 - (1 - u)^{\frac{1}{b}} \right)^{\frac{1}{a}}$$
    where $a$ and $b$ are shape parameters.
    \item \textbf{Arcsine Distribution:} Using the inverse transform for this special case of the Beta distribution:
    $$x = \sin^2\left(\frac{\pi u}{2}\right)$$
\end{itemize}

\noindent \textbf{Planned Outputs:}
The application will generate:
\begin{itemize}
    \item A scatter plot of the generated samples.
    \item A histogram of the simulated data overlaid with the theoretical density curve (PDF).
    \item A summary table comparing the Simulated Mean and Variance vs. the Theoretical Mean and Variance.
    \item A Q-Q plot to visually assess the goodness-of-fit.
\end{itemize}

\section{User Inputs (Shiny Components)}
Users will be able to modify the following:
\begin{enumerate}
    \item \textbf{Setting the seed:} To ensure the simulation results are reproducible.
    \item \textbf{Change the parameters:} Specifically, for the Kumaraswamy distribution, users can adjust the shape parameters $a$ and $b$ (where $a, b > 0$).
    \item \textbf{Select the information presented:}
    \begin{itemize}
        \item The mean and variance comparison (Simulated vs Theoretical),
        \item Histogram and Q-Q plot for goodness-of-fit,
        \item And the scatterplot of the samples generated.
    \end{itemize}
    \item \textbf{Toggle Distribution Views:} Be able to choose which distribution to simulate (switch between Kumaraswamy and Arcsine) or potentially compare them side-by-side.
    \item \textbf{Plot Customization:} Be able to modify the colours of the histograms and density lines.
    \item \textbf{Download Data:} An option to download the currently simulated dataset as a .csv file.
\end{enumerate}

\end{normalsize}

% --- REFERENCES SECTION ---
\bibliographystyle{abbrvnat}
\bibliography{bibliography} 

% Forces these citations to appear even if not explicitly referenced in text
\nocite{RCoreTeam}
\nocite{shiny}
\nocite{voss2013intro}
\nocite{white2015template}

\end{document}